Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-13 tsibbletalk.Rmd
minor tweaks

R \CRANpkg{shiny} [@R-shiny] and \CRANpkg{htmlwidgets} [@R-htmlwidgets] lay a fundamental infrastructure in marrying R with HTML elements and Javascript for interactivity, although they do not emphasise on interactive graphics. The \CRANpkg{htmlwidgets} package opens a door to embedding Javascript libraries into R such that users are able to write only R code to generate web-based plots. Many Javascript charting libraries have been ported to R as HTML widgets, including \CRANpkg{plotly} [@plotly2020], \CRANpkg{rbokeh} [@R-rbokeh], and \CRANpkg{leaflet} [@R-leaflet] for maps. To enable interactions between different widgets, it can be achieved with \CRANpkg{shiny} or \CRANpkg{crosstalk} [@R-crosstalk]. The \CRANpkg{crosstalk} extends \CRANpkg{htmlwidgets} with shared R6 instances to support linked brushing and filtering across widgets, without relying on \CRANpkg{shiny}.

@@

This shiny module, decoupled to `tsibbleWrapUI()` and `tsibbleWrapServer()`, presents a clean interface and forms a resusable piece in a shiny application. A shiny module provides the vehicle in modularising shiny applications for both users and developers. Like all shiny modules, the first argument in both functions requires a user-supplied session id that must be unique. The UI function `tsibbleWrapUI()` simply shows a slider that animates or controls the number of periods to be diced. The workhorse is certainly the server function `tsibbleWrapServer()`, encapsulating the algorithm that transforms data and sends messages to update the plot accordingly. The `plot` argument expects a `ggplot` or `plotly` object, where one can plot data using either lines or other graphical elements (such as boxplots). As the function name suggests, a (shared) tsibble is needed to start the engine, and thereby the time `index` can be retrieved for dissection. The `period` option semantically takes a desired number of seasonal periods to be shifted, for example data shifted by "1 day", "2 days", or "1 week", etc. In other words, the `period` defines the grind level. As for date-times (represented by `POSIXt`), it ranges from from fine "day" to coarse "year". The following code snippet generates Figure \ref{fig:wrap-ped}.

>>>>

R \CRANpkg{shiny} [@R-shiny] and \CRANpkg{htmlwidgets} [@R-htmlwidgets] lay a fundamental infrastructure in marrying R with HTML elements and Javascript for interactivity, although they seldom emphasise on interactive graphics. The \CRANpkg{htmlwidgets} package opens a door to embedding Javascript libraries into R such that users are able to write only R code to generate web-based plots. Many Javascript charting libraries have been ported to R as HTML widgets, including \CRANpkg{plotly} [@plotly2020], \CRANpkg{rbokeh} [@R-rbokeh], and \CRANpkg{leaflet} [@R-leaflet] for maps. To enable interactions between different widgets, it can be achieved with \CRANpkg{shiny} or \CRANpkg{crosstalk} [@R-crosstalk]. The \CRANpkg{crosstalk} extends \CRANpkg{htmlwidgets} with shared R6 instances to support linked brushing and filtering across widgets, without relying on \CRANpkg{shiny}.

@@

This shiny module, decoupled to `tsibbleWrapUI()` and `tsibbleWrapServer()`, presents a clean interface and forms a resusable piece in a shiny application. A shiny module provides the vehicle in modularising shiny applications for both users and developers. Like all shiny modules, the first argument in both functions requires a user-supplied session id that must be unique. The UI function `tsibbleWrapUI()` simply shows a slider that animates or controls the number of periods to be diced. The workhorse is certainly the server function `tsibbleWrapServer()`, encapsulating the algorithm that transforms data and sends messages to update the plot accordingly. The `plot` argument expects a `ggplot` or `plotly` object, where one can plot data using either lines or other graphical elements (such as boxplots). As the function name suggests, a (shared) tsibble is needed to start the engine, and thereby the time `index` can be retrieved for dissection. The `period` option semantically takes a desired number of seasonal periods to be shifted, for example data shifted by "1 day", "2 days", or "1 week", etc. In other words, the `period` defines the grind level. For date-times (represented by `POSIXt`), the adjustment ranges from from fine "day" to coarse "year". The following code snippet generates Figure \ref{fig:wrap-ped}.
